---
title: "6 months_prior"
author: "Madhawa Hulangamuwa"
date: "11/8/2021"
output: html_document
---

## Political Incidents Considered

## 10 octomber 2000 - Parliament election
## 05 December 2001 - Parliament election
## 02 April 2004 - Parliament election
## 17 November 2005 - Mahinda rajapaksha became the president-Presidential election
## 26 January 2010 - Mahinda Rajapaksha re-elected as the president
## 08 & 20 April 2010 - Mahinda rajapaksha's party wins parliamentry election
## 8 september 2010 Approves consitutional change in parliament allowing Mahinda Rajapaksha to seek unlimited number of terms.
## 15 January 2015- Maithripala Sirisena elected as the president.
## 17 August 2015 Parliament election 
## 26 Octomber 2018 to 16 December 2018 - Constitutional crisis 
## 10 November 2019 - Gotabaya Rajapaksha elected as president.
## 05 August 2020 - Rajapaksha's party wins the parliamentry Election.


```{r}

library(readxl)
library(writexl)

CSE_data <- read_excel("CSE.xlsx")
CSE <- CSE_data[!CSE_data$Close == "null", ]
View(CSE)

CSE$Open <- as.numeric(CSE$Open)
CSE$High <- as.numeric(CSE$High)
CSE$Low <- as.numeric(CSE$Low)
CSE$Close <- as.numeric(CSE$Close)
CSE$`Adj Close` <- as.numeric(CSE$`Adj Close`)
CSE$Volume <- as.numeric(CSE$Volume)
CSE$Date <- as.Date(CSE$Date)
str(CSE)



```

## ## Adding Factor to dataset(pltInf = 1 6 months prior election time  and 6 months after incident, pltInf = 0 otherwise.)


```{r}

#CSE$pltInf <- 0
#View(CSE)

```

## 


```{r}
library(dplyr)
library(tidyr)


incident <- CSE[CSE$Date >= "2000-04-10" & CSE$Date <= "2001-04-10" | 
                CSE$Date >= "2001-06-05" & CSE$Date <= "2002-06-05" |
                CSE$Date >= "2003-10-02" & CSE$Date <= "2004-10-02" |
                CSE$Date >= "2005-05-17" & CSE$Date <= "2006-05-17" |
                CSE$Date >= "2009-07-26" & CSE$Date <= "2010-07-26" |
                CSE$Date >= "2009-10-08" & CSE$Date <= "2010-10-20" |
                CSE$Date >= "2010-03-08" & CSE$Date <= "2011-03-08" |
                CSE$Date >= "2014-07-15" & CSE$Date <= "2015-07-15" |
                CSE$Date >= "2015-02-17" & CSE$Date <= "2016-02-17" |
                CSE$Date >= "2018-04-26" & CSE$Date <= "2018-06-16" |
                CSE$Date >= "2019-05-10" & CSE$Date <= "2020-05-10" |
                CSE$Date >= "2020-02-05" & CSE$Date <= "2021-02-05"
                ,]

new_CSE <- CSE %>% mutate(pltInf=as.factor(if_else(CSE$Date %in% incident$Date, 1, 0)))

str(new_CSE)
View(new_CSE)



```

```{r}

write_xlsx(new_CSE,"C:\\Users\\Madhawa Hulangamuwa\\Desktop\\6 Months Prior//Data.xlsx")
write.csv(new_CSE,"C:\\Users\\Madhawa Hulangamuwa\\Desktop\\6 Months Prior//Data.csv", row.names = FALSE)


```
