---
title: "provincial_council_14 days_prior"
author: "Madhawa Hulangamuwa"
date: "11/11/2021"
output: html_document
---

## Provincial Council Elections – 2014/March/29 (Uva , Southern)
## Provincial Council Elections – 2013/september/21 (Northern , North Western)
## Provincial Council Elections – 2012/September/08 (Eastern, North Central, Sabaragamuwa)
## Provincial Council Elections – 2009/February/14 (Southern, Uva, Western, Central & North Western)
## Provincial Council Elections – 2008/May/10 (Sabaragamuwa & North Central, Eastern)
## Provincial Council Elections – 2004/April/24

```{r}

library(readxl)
library(writexl)

CSE_data <- read_excel("CSE.xlsx")
CSE <- CSE_data[!CSE_data$Close == "null", ]
View(CSE)

CSE$Open <- as.numeric(CSE$Open)
CSE$High <- as.numeric(CSE$High)
CSE$Low <- as.numeric(CSE$Low)
CSE$Close <- as.numeric(CSE$Close)
CSE$`Adj Close` <- as.numeric(CSE$`Adj Close`)
CSE$Volume <- as.numeric(CSE$Volume)
CSE$Date <- as.Date(CSE$Date)
str(CSE)



```

## R Markdown

```{r}

library(dplyr)
library(tidyr)


incident <- CSE[CSE$Date >= "2014-03-15" & CSE$Date <= "2014-04-13" | 
                 CSE$Date >= "2013-09-07" & CSE$Date <= "2013-10-05" |
                 CSE$Date >= "2012-08-23" & CSE$Date <= "2012-09-22" |
                 CSE$Date >= "2010-01-31" & CSE$Date <= "2006-02-28" |
                 CSE$Date >= "2008-04-26" & CSE$Date <= "2008-05-24" |
                 CSE$Date >= "2004-04-10" & CSE$Date <= "2004-05-08"
                 ,]

new_CSE <- CSE %>% mutate(pltInf=as.factor(if_else(CSE$Date %in% incident1$Date, 1, 0)))

str(new_CSE)
View(new_CSE)



```





```{r}

write_xlsx(new_CSE,"C:\\Users\\Madhawa Hulangamuwa\\Desktop\\14_Days prior Provincial//Data.xlsx")
write.csv(new_CSE,"C:\\Users\\Madhawa Hulangamuwa\\Desktop\\14_Days prior Provincial//Data.csv", row.names = FALSE)


```