---
title: "14 days prior"
author: "Madhawa Hulangamuwa"
date: "11/8/2021"
output: html_document
---


## Political Incidents Considered

## 10 octomber 2000 - Parliament election
## 05 December 2001 - Parliament election
## 02 April 2004 - Parliament election
## 17 November 2005 - Mahinda rajapaksha became the president-Presidential election
## 26 January 2010 - Mahinda Rajapaksha re-elected as the president
## 08 & 20 April 2010 - Mahinda rajapaksha's party wins parliamentry election
## 8 september 2010 Approves consitutional change in parliament allowing Mahinda Rajapaksha to seek unlimited number of terms.
## 15 January 2015- Maithripala Sirisena elected as the president.
## 17 August 2015 Parliament election 
## 26 Octomber 2018 to 16 December 2018 - Constitutional crisis 
## 10 November 2019 - Gotabaya Rajapaksha elected as president.
## 05 August 2020 - Rajapaksha's party wins the parliamentry Election.

```{r setup, include=FALSE}

library(readxl)
library(writexl)

CSE_data <- read_excel("CSE.xlsx")
CSE <- CSE_data[!CSE_data$Close == "null", ]
View(CSE)

CSE$Open <- as.numeric(CSE$Open)
CSE$High <- as.numeric(CSE$High)
CSE$Low <- as.numeric(CSE$Low)
CSE$Close <- as.numeric(CSE$Close)
CSE$`Adj Close` <- as.numeric(CSE$`Adj Close`)
CSE$Volume <- as.numeric(CSE$Volume)
CSE$Date <- as.Date(CSE$Date)
str(CSE)

```

## 



```{r cars}

library(dplyr)
library(tidyr)


incident3 <- CSE[CSE$Date >= "2000-09-26" & CSE$Date <= "2000-10-24" | 
                CSE$Date >= "2001-11-21" & CSE$Date <= "2002-12-19" |
                CSE$Date >= "2004-03-19" & CSE$Date <= "2004-04-16" |
                CSE$Date >= "2005-11-03" & CSE$Date <= "2005-12-01" |
                CSE$Date >= "2010-01-12" & CSE$Date <= "2010-01-13" |
                CSE$Date >= "2010-03-23" & CSE$Date <= "2010-05-04" |
                CSE$Date >= "2010-08-23" & CSE$Date <= "2011-09-22" |
                CSE$Date >= "2015-01-01" & CSE$Date <= "2015-01-29" |
                CSE$Date >= "2015-08-03" & CSE$Date <= "2016-09-01" |
                CSE$Date >= "2018-11-12" & CSE$Date <= "2019-12-10" |
                CSE$Date >= "2019-10-26" & CSE$Date <= "2019-11-24" |
                CSE$Date >= "2020-07-21" & CSE$Date <= "2020-08-19"
                ,]

new_CSE3 <- CSE %>% mutate(pltInf=as.factor(if_else(CSE$Date %in% incident3$Date, 1, 0)))

str(new_CSE3)
View(new_CSE3)

```

## Including Plots

You can also embed plots, for example:

```{r}

write_xlsx(new_CSE3,"C:\\Users\\Madhawa Hulangamuwa\\Desktop\\14 Days Prior//Data.xlsx")
write.csv(new_CSE3,"C:\\Users\\Madhawa Hulangamuwa\\Desktop\\14 Days Prior//Data.csv", row.names = FALSE)


```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
