---
title: "3 months_prior"
author: "Madhawa Hulangamuwa"
date: "11/8/2021"
output: html_document
---

## Political Incidents Considered

## 10 octomber 2000 - Parliament election
## 05 December 2001 - Parliament election
## 02 April 2004 - Parliament election
## 17 November 2005 - Mahinda rajapaksha became the president-Presidential election
## 26 January 2010 - Mahinda Rajapaksha re-elected as the president
## 08 & 20 April 2010 - Mahinda rajapaksha's party wins parliamentry election
## 8 september 2010 Approves consitutional change in parliament allowing Mahinda Rajapaksha to seek unlimited number of terms.
## 15 January 2015- Maithripala Sirisena elected as the president.
## 17 August 2015 Parliament election 
## 26 Octomber 2018 to 16 December 2018 - Constitutional crisis 
## 10 November 2019 - Gotabaya Rajapaksha elected as president.
## 05 August 2020 - Rajapaksha's party wins the parliamentry Election.

```{r}

library(readxl)
library(writexl)

CSE_data <- read_excel("CSE.xlsx")
CSE <- CSE_data[!CSE_data$Close == "null", ]
View(CSE)

CSE$Open <- as.numeric(CSE$Open)
CSE$High <- as.numeric(CSE$High)
CSE$Low <- as.numeric(CSE$Low)
CSE$Close <- as.numeric(CSE$Close)
CSE$`Adj Close` <- as.numeric(CSE$`Adj Close`)
CSE$Volume <- as.numeric(CSE$Volume)
CSE$Date <- as.Date(CSE$Date)
str(CSE)

```

## Data

```{r cars}

library(dplyr)
library(tidyr)


incident1 <- CSE[CSE$Date >= "2000-07-10" & CSE$Date <= "2001-01-10" | 
                CSE$Date >= "2001-09-05" & CSE$Date <= "2002-03-05" |
                CSE$Date >= "2004-01-02" & CSE$Date <= "2004-07-02" |
                CSE$Date >= "2005-08-17" & CSE$Date <= "2006-02-17" |
                CSE$Date >= "2009-10-26" & CSE$Date <= "2010-04-26" |
                CSE$Date >= "2010-01-08" & CSE$Date <= "2010-07-20" |
                CSE$Date >= "2010-06-08" & CSE$Date <= "2011-12-08" |
                CSE$Date >= "2014-10-15" & CSE$Date <= "2015-04-15" |
                CSE$Date >= "2015-05-17" & CSE$Date <= "2016-11-17" |
                CSE$Date >= "2018-07-26" & CSE$Date <= "2019-03-16" |
                CSE$Date >= "2019-08-10" & CSE$Date <= "2020-02-10" |
                CSE$Date >= "2020-05-05" & CSE$Date <= "2020-11-05"
                ,]

new_CSE1 <- CSE %>% mutate(pltInf=as.factor(if_else(CSE$Date %in% incident1$Date, 1, 0)))

str(new_CSE1)
View(new_CSE1)


```
 
## Export

```{r}

write_xlsx(new_CSE1,"C:\\Users\\Madhawa Hulangamuwa\\Desktop\\3 Months Prior//Data.xlsx")
write.csv(new_CSE1,"C:\\Users\\Madhawa Hulangamuwa\\Desktop\\3 Months Prior//Data.csv", row.names = FALSE)


```


