---
title: "Provisncial Council"
author: "Madhawa Hulangamuwa"
date: "11/10/2021"
output: html_document
---


## Provincial Council Elections – 2014/March/29 (Uva , Southern)
## Provincial Council Elections – 2013/september/21 (Northern , North Western)
## Provincial Council Elections – 2012/September/08 (Eastern, North Central, Sabaragamuwa)
## Provincial Council Elections – 2009/February/14 (Southern, Uva, Western, Central & North Western)
## Provincial Council Elections – 2008/May/10 (Sabaragamuwa & North Central, Eastern)
## Provincial Council Elections – 2004/April/24

```{r}

library(readxl)
library(writexl)

CSE_data <- read_excel("CSE.xlsx")
CSE <- CSE_data[!CSE_data$Close == "null", ]
View(CSE)

CSE$Open <- as.numeric(CSE$Open)
CSE$High <- as.numeric(CSE$High)
CSE$Low <- as.numeric(CSE$Low)
CSE$Close <- as.numeric(CSE$Close)
CSE$`Adj Close` <- as.numeric(CSE$`Adj Close`)
CSE$Volume <- as.numeric(CSE$Volume)
CSE$Date <- as.Date(CSE$Date)
str(CSE)



```

## R Markdown

```{r}

library(dplyr)
library(tidyr)


incident3 <- CSE[CSE$Date >= "2013-12-29" & CSE$Date <= "2014-06-29" | 
                CSE$Date >= "2013-06-21" & CSE$Date <= "2013-12-21" |
                CSE$Date >= "2012-06-08" & CSE$Date <= "2012-12-08" |
                CSE$Date >= "2009-11-14" & CSE$Date <= "2006-05-14" |
                CSE$Date >= "2008-02-10" & CSE$Date <= "2008-08-10" |
                CSE$Date >= "2004-01-24" & CSE$Date <= "2004-07-24"
                ,]

new_CSE3 <- CSE %>% mutate(pltInf=as.factor(if_else(CSE$Date %in% incident3$Date, 1, 0)))

str(new_CSE3)
View(new_CSE3)



```





```{r}

write_xlsx(new_CSE3,"C:\\Users\\Madhawa Hulangamuwa\\Desktop\\3_months prior Provincial//Data.xlsx")
write.csv(new_CSE3,"C:\\Users\\Madhawa Hulangamuwa\\Desktop\\3_months prior Provincial//Data.csv", row.names = FALSE)


```

